TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-13 paper/draft.tex
use crv scatters

\subsubsection{Spectral Type Model \label{subsec:west_results}}
We trained \thecannon\ on 51 M dwarfs with a one-dimensional spectral type label, and obtained a precision of $\pm$0.6 spectral types, more precise than the original training label uncertainty of $\pm$1 spectral type. We note however, that the training sample is distributed heavily towards earlier type sources, with a median spectral type of 3 and only one M8 and one M9 source. As seen in Figure \ref{fig:west_validation}, the model performs well at re-deriving the labels for the M8 and M9 source when they are included in the model (less than 1 SPT difference), but badly when left out (over 2 SPT difference), which indicates \thecannon\ does a poor job at extrapolating to labels outside of the training sample space.

>>>>

\subsubsection{Spectral Type Model \label{subsec:west_results}}
We trained \thecannon\ on 51 M dwarfs with a one-dimensional spectral type label, and obtained a precision of $\pm$0.9 spectral types, also similar to the original training label uncertainty of $\pm$1 spectral type. We note however, that the training sample is distributed heavily towards earlier type sources, with a median spectral type of 3 and only one M8 and one M9 source. As seen in Figure \ref{fig:west_validation}, the model performs well at re-deriving the labels for the M8 and M9 source when they are included in the model (less than 1 SPT difference), but badly when left out (over 2 SPT difference), which indicates \thecannon\ does a poor job at extrapolating to labels outside of the training sample space.
